The problem and promise of scale in multilayer networks

### 2019-12-08 paper/introduction.Rmd
more spatial

<!-- Social proximity scale 
sociality exists 
-->
Sociality is important because conspecifics have positive and negative benefits

@@

<!-- Regular networks
* SNA significant outcomes
-->

<!-- Multilayer networks
used across disciplines
-->
Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a]. They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a]. <!--GENERALLY INTERESTING Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].-->

@@

<!-- Case study 
deer
fogo caribou
-->

>>>>

<!-- ### Social proximity scale 
sociality exists 
-->
Sociality is important because conspecifics have positive and negative benefits

@@

<!-- ### Regular networks
* SNA significant outcomes
-->
Network theory and social network analysis allows one to scale across dyads, groups, etc from pairwise interactions to social units, networks etc[@krause2009]

infer process from large scale pattern [@krause2009]

Structure of social networks affects evolutionary processes, population dynamics, [@kurvers2014]

<!-- ### Multilayer networks
used across disciplines
-->
Multilayer networks explicitly consider social systems across temporal, spatial and social contexts [@pilosof2017a]. They are made up of multiple layers, each representing relationships, individuals, spatial areas or temporal windows [@kivela2014; @porter2018a]. <!--GENERALLY INTERESTING Recently used in animal behaviour studies, multilayer networks have the potential to better characterize complex social systems [@silk2018a; @finn2019].-->

@@

<!-- ### Case study 
deer
fogo caribou
-->
